---
title: "Model runs report for Spatial BRP MS"
author: "Bosley et al. SPASAM"
date: '`r format(Sys.time(), "%d %B, %Y")`'
output:
  pdf_document: default
  html_document: default
geometry: margin=1in
---

```{r,echo = F, warning = F, comment = F, message=F}
#setting global options for the analysis log
library(knitr)
knitr::opts_chunk$set(tidy.opts=list(width.cutoff=70),tidy=TRUE, fig.width=6,
fig.height=5, warning=FALSE, message=FALSE)

# When tables are made no comments
options(xtable.comment = FALSE)

# load.packages
library(pander)
library(ggplot2)
library(tidyr)
library(reshape2)
library(ggmap)
library(xtable)
library(data.table)
library(PBSmodelling)
library(maps)
library(mapdata)
library(ggmap)

```
\
\


### HAKE
The following plot and tables show model specifications and results for hake model runs
\


### **Parameter values for mat/selectivity**

```{r, echo = F, results = "asis",include.rownames = FALSE}
wd<-getwd()
setwd(wd)
hake<-read.csv("HakeParams.csv")
panderOptions("table.style", "rmarkdown")
pandoc.table(hake, split.cells=10)
```
\newpage


### **Parameter values apportionment**

```{r, xtable, echo = F, results = "asis",include.rownames = FALSE}
hake.move<-read.csv("Hake_movement.csv")
cat("Primary Movement")
panderOptions("table.style", "simple")
pandoc.table(hake.move, split.cells=10, keep.line.breaks = TRUE, missing = "")

cat("Alternate Movement")
hake.move.alt<-read.csv("Hake_movement_Alt.csv")
pandoc.table(hake.move.alt, split.cells=10, keep.line.breaks = TRUE, missing = "")

```
\newpage


### **Parameter values apportionment**

```{r table2, echo=FALSE, message=FALSE, warnings=FALSE, results='asis'}
tabl <- " Hake recruitment apportionment by model run

| Model | Area 1(S)  | Area 2(N)  |  
|:------:|:---------:|:------:|
|   G & B |  0.3  |    0.7    |    
|  SPASAM  |  0.9  |   0.1   |
|  SPASAM - alt  |  0.8  |   0.2   |
"
cat(tabl) # output the table in a format good for HTML/PDF/docx conversion
```

\newpage


### Looking at maturity values
\
\
```{r, echo = F}

#melt data for ggplot
mat <- melt(hake[,c(1,6,7,8,9)], id="Age")
ggplot(mat,aes(Age,value, col = variable ))+
  geom_line(lwd = 1)+
  geom_point(size  = 1.8)+
  scale_color_manual(values = c("red","blue","limegreen","grey40"), labels=c("SPASAM-South","SPASAM-North","Panmictic","G&B"))+
  ylab("Maturity")+
  theme_bw()+
  theme(legend.title = element_blank())+
  ggtitle("Maturity by Area")

```

\newpage



### Looking at selectivity values
\
\

```{r,echo=F}
sel <- melt(hake[,c(1,10,11,12)], id="Age")
ggplot(sel,aes(Age,value, col = variable ))+
  geom_line(lwd = 1)+
  geom_point(size  = 1.8)+
  scale_color_manual(values = c("red","blue","grey40"), labels=c("SPASAM Fishery Sel","SPASAM Survey Sel","G&B Fishery Sel"))+
  ylab("Selectivity")+
  theme_bw()+
  theme(legend.title = element_blank())+
  ggtitle("Selectivity by Type")
```

\newpage


### Specifications for model runs
\
```{r, echo = F,results = 'asis'}
results<-read.csv("MSY_True_results.csv")
print(xtable(results[,1:2]),include.rownames = FALSE)
      
#panderOptions("table.style", "rmarkdown")
#pandoc.table(results[,1:2], split.cells = c(5,500))
```
\newpage
\
\


### Model run results
\
\
In these plots the red diamonds represent South (Area 1) and the blue squares represent North (Area 2). Red dotted lines and black circles are the panmictic population levels @ MSY. Population totals aggregated over areas are represented in grey.


1. F for each area
\
```{r, echo = F, fig.width = 8, fig.height = 6}
#create a vector of model runs
model.names<-results[,1]
runN<-1:length(model.names)
pan<-grep("panmictic",results[,2])

#create the plot
{par(mar = c(5,5,5,5))
plot(runN,results$F.1, pch = 21, cex = 1.8, bg = "grey", ylab = "Fishing Mortality", xaxt = "n", xlab = " ", ylim = c(0,1.2),type = "n")
abline(h = results$F.1[pan], lty = 2, col = "red") # panmictic MSY
axis(side = 1, at = runN, labels = FALSE, tck = -0.02)
text(runN,par("usr")[3]-0.02, labels = model.names, srt = 40, pos = 1, xpd = TRUE)


points(runN,results$F.1, pch = 23, bg = "red",cex = 1.2) 
points(runN,results$F.2, pch = 22, bg = "blue", cex = 1.2) 
points(runN[pan],results$F.1[pan], pch = 16, col = "black", cex = 1.3)

par(xpd = T)
legend(22,1.2,legend = c("1","2","P"),bty = 'n', pch = c(23,22,16), pt.bg = c("red","blue","black"),title = "Area")}
model.names2<-as.character(model.names[-c(3,4,5,6,13,17,21)])
results2<-results[-c(2,3,4,5,6,13,17),]
model.names2 <- factor(model.names2, levels = model.names2[order(levels(model.names2))])
temp<-melt(cbind(results2[,c("F.1","F.2")],model.names2))
names(temp)<-c("Scenario","Area","F")
ggplot(temp)+geom_point(aes(x=Scenario,y=F,colour=Area,shape=Area),size=3)+geom_hline(aes(yintercept=results$F.1[pan]))+ theme_bw()+ ggtitle("Fishing mortality relative to panmictic")+scale_color_manual(values=c("red","blue"))+ylab("Fishing mortality")

```
\
\
\
\
\newpage
2.Total equilibrium biomass
\
```{r, echo = F, fig.width = 8, fig.height = 6}
{plot(runN,results$biomass_total_end, pch = 16, cex = 1.8, bg = "grey", ylab = "Equilibrium Biomass", xaxt = "n", xlab = " ",ylim = c(0,3000000),type = "n")
  
abline(h = results$biomass_total_end[pan], lty = 2, col = "red")
axis(side = 1, at = runN, labels = FALSE, tck = -0.02)
text(runN,par("usr")[3]-0.02, labels = model.names, srt = 40, pos = 1, xpd = TRUE)
points(runN,results$biomass_total_end, pch = 21, bg = "grey",cex = 1.8)
points(runN[pan],results$biomass_total_end[pan], pch = 16, col = "black", cex = 1.2)} 

###########ggplot version
temp<-data.frame(cbind(results2$biomass_total_end))
names(temp)<-c("Biomass")
temp$Scenario <- factor(model.names2,levels=model.names2)
temp$Biomass<-as.numeric(temp$Biomass)/1000000
ggplot(temp)+geom_point(aes(x=Scenario,y=Biomass),size=4,colour="dark grey")+geom_hline(aes(yintercept=results$biomass_total_end[pan]/1000000))+ theme_bw()+ ggtitle("Equilibrium biomass relative to panmictic")+scale_color_manual(values=c("red","blue"))+ylab("Equilibrium biomass (mmt)")+expand_limits(y = 0)


#panmictic
```
\
\
\newpage
3.Yield
\
```{r, echo = F, fig.width = 8, fig.height = 6}
options(scipen = 50, digits = 4)
{par(mar = c(5,5,5,5))
plot(runN,results$yield_total, pch = 21, cex = 1.8, bg = "grey", ylab = "Yield", xaxt = "n", xlab = " ", ylim = c(0,600000))
abline(h = results$yield_total[pan], lty = 2, col = "red") # panmictic MSY
points(runN,results$yield_total, pch = 21, cex = 1.8, bg = "grey")
axis(side = 1, at = runN, labels = FALSE, tck = -0.02)

#add area specific values
points(runN,results$yield_region.1, pch = 23, bg = "red") 
points(runN,results$yield_region.2, pch = 22, bg = "blue") 
points(runN[pan],results$yield_total[pan], pch = 16, col = "black", cex = 1.2) #panmictic

#add legend
par(xpd = T)
text(runN,par("usr")[3]-0.02, labels = model.names, srt = 40, pos = 1, xpd = TRUE)
legend(22,600000,legend = c("T","1","2","P"),bty = 'n', pch = c(21,23,22,16), pt.bg = c("grey","red","blue", "black"),title = "Area")}###########ggplot version
####
##### ggplot

temp<-cbind(results2[,c("yield_total","yield_region.1","yield_region.2")])
names(temp)<-c("Total","Region.1","Region.2")
temp$Scenario <- factor(model.names2,levels=model.names2)
temp<-melt(temp)
names(temp)<-c("Scenario","Area","Yield")
ggplot(temp)+geom_point(aes(x=Scenario,y=Yield,colour=Area,shape=Area),size=3)+geom_hline(aes(yintercept=results$yield_total[pan]))+ theme_bw()+ ggtitle("Yield relative to panmictic")+scale_color_manual(values=c("grey","blue","green"))
#+ylab("Yield")




```
\
\
\newpage
4. Depletion
\
```{r, echo = F, fig.width = 8, fig.height = 6}
options(scipen = 50, digits = 4)

{par(mar=c(5,5,5,5))
plot(runN,results$depletion_total, pch = 21, cex = 1.8, bg = "grey", ylab = "Depletion", xaxt = "n", xlab = " ", ylim = c(0,1))
abline(h = results$depletion_total[pan], lty = 2, col = "red") # panmictic MSY
points(runN,results$depletion_total, pch = 21, cex = 1.8, bg = "grey")
axis(side = 1, at = runN, labels = FALSE, tck = -0.02)

#add area specific values
points(runN,results$depletion_region.1, pch = 23, bg = "red") 
points(runN,results$depletion_region.2, pch = 22, bg = "blue") 
points(runN[pan],results$depletion_total[pan], pch = 16, col = "black", cex = 1.2) #panmictic

#add legend
par(xpd = T)
text(runN,par("usr")[3]-0.02, labels = model.names, srt = 40, pos = 1, xpd = TRUE)
legend(22,1,legend = c("T","1","2","P"),bty = 'n', pch = c(21,23,22,16), pt.bg = c("grey","red","blue", "black"),title = "Area")}

###ggplot the same
temp<-cbind(results2[,c("depletion_total","depletion_region.1","depletion_region.2")])
temp$Scenario <- factor(model.names2,levels=model.names2)
names(temp)<-c("Total","Region.1","Region.2","Scenario")
temp<-melt(temp)
temp$Scenario <- factor(model.names2,levels=model.names2)
names(temp)<-c("Scenario","Area","Depletion")
ggplot(temp)+geom_point(aes(x=Scenario,y=Yield,colour=Area,shape=Area),size=3)+geom_hline(aes(yintercept=results$depletion_total[pan]))+ theme_bw()+ ggtitle("Depletion relative to panmictic")+scale_color_manual(values=c("grey","blue","green"))
#+ylab("Yield")



\
\
\newpage
5. SSB 
\
```{r, echo = F, fig.width = 8, fig.height = 6}
options(scipen = 50, digits = 4)
{par(mar=c(5,5,5,5))
plot(runN,results$SSB_total_end, pch = 21, cex = 1.8, bg = "grey", ylab = "SSB", xaxt = "n", xlab = " ", ylim = c(0,1200000))
abline(h = results$SSB_total_end[pan], lty = 2, col = "red") # panmictic MSY
points(runN,results$SSB_total_end, pch = 21, cex = 1.8, bg = "grey")
axis(side = 1, at = runN, labels = FALSE, tck = -0.02)

#add area specific values
points(runN,results$SSB_end_region.1, pch = 23, bg = "red") 
points(runN,results$SSB_end_region.2, pch = 22, bg = "blue") 
points(runN[pan],results$SSB_total_end[pan], pch = 16, col = "black", cex = 1.2) #panmictic

#add legend
par(xpd = T)
text(runN,par("usr")[3]-0.02, labels = model.names, srt = 40, pos = 1, xpd = TRUE)
legend(22,1200000,legend = c("T","1","2","P"),bty = 'n', pch = c(21,23,22,16), pt.bg = c("grey","red","blue", "black"),title = "Area")}

###ggplot the same
temp<-cbind(results2[,c("SSB_total_end","SSB_end_region.1","SSB_end_region.2")])
temp$Scenario <- factor(model.names2,levels=model.names2)
names(temp)<-c("Total","Region.1","Region.2","Scenario")
temp<-melt(temp)
temp$Scenario <- factor(model.names2,levels=model.names2)
names(temp)<-c("Scenario","Area","SSB")
temp$SSB<-temp$SSB/1000000
ggplot(temp)+geom_point(aes(x=Scenario,y=SSB,colour=Area,shape=Area),size=3)+geom_hline(aes(yintercept=results$SSB_total_end[pan]))+ theme_bw()+ ggtitle("SSB relative to panmictic")+scale_color_manual(values=c("grey","blue","green"))
#+ylab("Yield")

```
\
\
\newpage
6. MSY Harvest rate
\
```{r, echo = F, fig.width = 8, fig.height = 6}
options(scipen = 50, digits = 4)
{par(mar=c(5,5,5,5))
plot(runN,results$u_region_total, pch = 21, cex = 1.8, bg = "grey", ylab = "Harvest Rate", xaxt = "n", xlab = " ", ylim = c(0,0.6))
abline(h = results$u_region_total[pan], lty = 2, col = "red") # panmictic MSY
points(runN,results$u_region_total, pch = 21, cex = 1.8, bg = "grey")
axis(side = 1, at = runN, labels = FALSE, tck = -0.02)

#add area specific values
points(runN,results$u_region.1, pch = 23, bg = "red") 
points(runN,results$u_region.2, pch = 22, bg = "blue") 
points(runN[pan],results$u_region_total[pan], pch = 16, col = "black", cex = 1.2) #panmictic

#add legend
par(xpd = T)
text(runN,par("usr")[3]-0.02, labels = model.names, srt = 40, pos = 1, xpd = TRUE)
legend(22,0.6,legend = c("T","1","2","P"),bty = 'n', pch = c(21,23,22,16), pt.bg = c("grey","red","blue", "black"),title = "Area")}

###ggplot the same
temp<-cbind(results2[,c("u_region_total","u_region.1","u_region.2")])
temp$Scenario <- factor(model.names2,levels=model.names2)
names(temp)<-c("Total","Region.1","Region.2","Scenario")
temp<-melt(temp)
temp$Scenario <- factor(model.names2,levels=model.names2)
names(temp)<-c("Scenario","Area","Exploitation")
ggplot(temp)+geom_point(aes(x=Scenario,y=Exploitation,colour=Area,shape=Area),size=3)+geom_hline(aes(yintercept=results$u_region_total[pan]))+ theme_bw()+ ggtitle("Exploitation rate relative to panmictic")+scale_color_manual(values=c("grey","blue","green"))
#+ylab("Yield")


```
\
\

###Stochasitic recruitment

```{r, echo = F, fig.width = 8, fig.height = 6}
options(scipen = 50, digits = 4)
out<-readList("Hake_stoch_rec.rep")
#names(stoch.rec)
biomass.total<-out$biomass_total
yield.total<-out$yield_total
years<-seq(1:200)

#Harvest

#{par(mfrow=c(2,1))
plot(years,biomass.total, type = "b", xlab = "Years", ylab = "Biomass", pch = 21, bg = "grey")
#plot(years,yield.total, type = "b", xlab = "Years", ylab = "Yield")}
```


###Stochasitic apportionment

```{r, echo = F, fig.width = 8, fig.height = 5}
par(mfrow=c(1,2))
options(scipen = 50, digits = 4)
{out<-readList("Hake_stoch_apport.rep")
#names(out)
recruits.BM.1<-out$recruits_BM[1,]
recruits.BM.2<-out$recruits_BM[2,]
yield.total<-out$yield_total
years<-seq(1:200)

#{par(mfrow=c(2,1))
{plot(years,recruits.BM.1, type = "b", xlab = "Years", ylab = "Recruitment", pch = 21, bg = "grey20", ylim =c(0,2900000), main = "Apportionment Deviations")
points(years,recruits.BM.2, type = "b", ylab = "Recruitment", pch = 21, bg = "grey80")}
#legend(180,1500000,legend = c("Area 1", "Area 2"),bty = 'n', pch = c(21,21), pt.bg = c("grey20","grey80"))}
#plot(years,yield.total, type = "b", xlab = "Years", ylab = "Yield")}

#uniform
out.u<-readList("Random_apport_uniform.rep")
#names(out)
recruits.BM.1<-out.u$recruits_BM[1,]
recruits.BM.2<-out.u$recruits_BM[2,]
yield.total<-out.u$yield_total
years<-seq(1:200)

#{par(mfrow=c(2,1))
{plot(years,recruits.BM.1, type = "b", xlab = "Years", ylab = "Recruitment", pch = 21, bg = "grey20", ylim =c(0,2900000), main = "Fully Random")
points(years,recruits.BM.2, type = "b", ylab = "Recruitment", pch = 21, bg = "grey80") }}
#legend(180,1500000,legend = c("Area 1", "Area 2"),bty = 'n', pch = c(21,21), pt.bg = c("grey20","grey80"))}
#plot(years,yield.total, type = "b", xlab = "Years", ylab = "Yield")}


```


## PHASE 2 Examples

```{r,echo = F,fig.width = 8, fig.height = 8, eval = F}
run1<-readList("C:\\Users\\katelyn.bosley\\Desktop\\Today\\HAKE\\Phase2\\Continuity_run1\\Spatial_BRP.rep")
run.corr<-readList("C:\\Users\\katelyn.bosley\\Desktop\\Today\\HAKE\\Phase2\\Continuity_run1\\Spatial_BRP_correct.rep")

#run1$harvest_rate_region_bio
#run1$harvest_rate_population_bio
#run1$yield_region
#run1$yield_population


{plot(years,run1$harvest_rate_region_bio[1,], type = "l", col = "red", lwd = 2, ylab = "Harvest Rate", ylim = c(0,1), xlab = "Years")
points(years,run1$harvest_rate_region_bio[2,], type = "l", col = "blue",lwd = 2)
points(years,run.corr$harvest_rate_region_bio[1,], type = "l", col = "grey20",lwd = 2)
points(years,run.corr$harvest_rate_region_bio[2,], type = "l", col = "grey20",lwd = 2,lty = 2)
legend("topright",legend = c("Test Area1","Test Area2","True Area1","True Area2"),lty = c(1,1,1,2), col =c ("red","blue","grey20","grey20"), lwd = c(2,2,2,2), bty = "n")}

```


### TAC allocation based on survey biomass
```{r,echo = F,fig.width = 8, fig.height = 8}
out.u1<-readList("TAC_Hake_Survey_low.rep")
out.u2<-readList("TAC_Hake_Survey_high.rep")
u.true = 0.227376
#names(out.u1)

#biomass
#par(mfrow = c(2,1))
{plot(years,out.u1$biomass_population, xlab = "Years",ylab = "Biomass", col = "grey50", pch = 16, ylim = c(1000000,6800000))
 points(years,out.u2$biomass_population, col = "blue")
 legend("topright",legend = c("low error", "high error"), col = c("grey50","blue"), pch = c(16,1))}


#harvest rate comparison
par(mfrow = c(2,1))
{plot(years,out.u1$harvest_rate_population_bio, xlab = "Years",ylab = "Harvest Rate (u)", main = "Low Error (SD = 0.2)", ylim = c(0,0.5))
abline(h = mean(out.u1$harvest_rate_population_bio), col = "red", lty = 2)
dif.1<-mean(out.u1$harvest_rate_population_bio)-u.true
text(20,0.5,paste("% dif = ",round(dif.1,5),sep = ""))

plot(years,out.u2$harvest_rate_population_bio, xlab = "Years",ylab = "Harvest Rate (u)", main = "High Error (SD = 0.5)", ylim = c(0,0.5))
abline(h = mean(out.u2$harvest_rate_population_bio), col = "red", lty = 2)
abline(h = u.true)
dif.2<-mean(out.u2$harvest_rate_population_bio)-u.true
text(20,0.5,paste("% dif = ",round(dif.2,5),sep = ""))
}

```

\newpage

### TAC Allocation based on Rec Index 

This time looking at yeild

```{r,echo = F,fig.width = 8, fig.height = 8}

rec.high<-readList("TAC_Rec_high.rep")
rec.low<-readList("TAC_Rec_low.rep")
Y.true<-552691

par(mfrow = c(2,1))

{{plot(years,rec.low$yield_population, xlab = "Years",ylab = "Yield", main = "Low Error (SD = 0.5")
abline(h = mean(rec.low$yield_population), col = "red", lty = 2)
abline(h = Y.true, col = "limegreen", lty = 2)
dif.1<-mean(rec.low$yield_population)-Y.true
text(180,1500000,paste("% dif = ",round(dif.1,5),sep = ""))}

#dif.1

{plot(years,rec.high$yield_population, xlab = "Years",ylab = "Yield", main = "High Error (SD = 0.8)")
abline(h = mean(rec.high$yield_population), col = "red", lty = 2)
abline(h = Y.true, col = "limegreen", lty = 2)
dif.2<-mean(rec.high$yield_population)-Y.true
text(180,1500000,paste("% dif = ",round(dif.2,5),sep = ""))}}

#dif.2
```

\newpage

###SABLEFISH

MSY_Search range for test = 0.005 - 0.8 by 0.05


```{r, echo = F,results = 'asis'}

tabl <- " Sablefish recruitment apportionment by model run

| Model | Area 1 | Area 2  | Area 3  |   
|:------:|:---------:|:------:|:-----:|
|   BASE |  0.4369  |  0.301 | 0.269 |   
"

cat(tabl)

sab<-read.csv("SablefishParams.csv")
mat <- melt(sab[,c(1,6,7)], id="Age")
#head(mat)

panderOptions("table.style", "rmarkdown")
pandoc.table(sab, split.cells=10)
```

\newpage
```{r,echo = F,fig.width = 8, fig.height = 5}

#plot for match/mismatch selectivity maturity by area

Area1<-melt(sab[,c(1,7,10)], id="Age")
Area2<-melt(sab[,c(1,7,13)], id="Age")
Area3<-melt(sab[,c(1,7,16)], id="Age")

Area1$area<-rep(1,nrow(Area1))
Area2$area<-rep(2,nrow(Area1))
Area3$area<-rep(3,nrow(Area1))

Sab.param<-rbind(Area1,Area2,Area3)


#plot Area1
ggplot(Sab.param,aes(Age,value, col = variable ))+
  geom_line(lwd = 1)+
  geom_point(size  = 1.8)+
  #scale_color_manual(values = c("red","black"), labels=c("Maturity","Fishery Sel"))+
  ylab("Maturity")+
  theme_bw()+
  theme(legend.title = element_blank())+
  ggtitle("Sablefish Parameters")+
  facet_wrap(~area)

```



###Menhaden





